Robust non-stationary local slope estimation

### 2021-12-13 ndip/paper.tex
Mon Dec 13 16:40:14 CST 2021

@@

\begin{keywords}
Seismic signal analysis, structural filtering, local slope
\end{keywords}

\section{Introduction}
The local slope is a seismic attribute that can be extracted from the raw data. It has been successfully applied in several geophysical processing and inverse problems, e.g., wavefield separation \cite{harlan1984signal,fomel2002pwd}, predictive painting \cite{fomel2010predictive}, velocity-independent seismic imaging \cite{fomel2007velocity}, regularized geophysical inversion \cite{fomel2007shape}, etc.

\new{The local slope is closely related with the seismic dip angle. Researchers have started the seismic dip estimation from last century. There are at least three-generations methods for calculating the seismic dip \cite{chopra2007volumetric}, e.g., (1) cross-correlation based methods \cite{browaeys2010local,aqrawi2012hybrid,aarre2013consistent}, (2) semblance-based discrete scanning methods \cite{marfurt19983,lou2019accurate}, (3) structure tensor-based methods \cite{hale2007local,wu2017directional,wang2018robust}.}

In the past decades, there have been a variety of slope estimation methods \new{based on the plane-wave theory}. The plane-wave destruction (PWD) method was originally proposed by \cite{claerbout1992pvi}. Fomel (2002) \cite{fomel2002pwd} proposed to use an implicit finite difference scheme to discretize the plane-wave equation, where an infinite impulse response (IIR) filter (also known as the all-pass filter) to approximate the phase-shift operator and transforms the plane-wave equation into a non-linear inverse problem. Hale (2007) \cite{hale2007local} proposed the structure-tensor, also known as the gradient tensor \cite{van1995estimators}, \old{based slope estimation method based}\new{where the slope estimation is based} on the assumption that eigenvector corresponding to the largest eigenvalue of the structure tensor \old{point}\new{points} to the structural direction.  Liu et al. (2015) \cite{liuyang2015} took advantage of the relation between 2D Hilbert transform and the derivatives of the seismic data and derive a fast non-iterative dip estimation method, which turns to be more robust than the PWD based slope estimation method in the case of noisy data \cite{yangkang2018gji3}. Chen et al. (2013) \cite{zhonghuan2013accelerated} accelerated the PWD method by deriving an analytical solution to the non-linear inverse problem based on the three-point all-pass approximation filter, thus the PWD method no longer requires outer-loop non-linear iterations and thus is significantly accelerated. Chen et al. (2013) \cite{zhonghuan2013omnidirectional} further improved the conventional PWD algorithm by proposing a circle-interpolating model that makes the PWD method avoid the aliasing issues, thereby well handling both vertical and horizontal structures.

The local slope of a seismic data can be used to compress the seismic events along the slope direction, i.e., to obtain an optimally sparse representation of the seismic data. This sparsification process is referred to as the seislet transform \cite{fomel2010seislet}. Since the seislet transform is based on the structure direction to compress the data, its sparsity in the transform domain highly depends on the accuracy of the estimated local slope. Chen (2016) \cite{yangkang2016emd} discussed the influence of the error of local slope estimation in the sparsity performance of the seislet transform, and developed a dip-separated processing strategy to deal with the limitation of the PWD algorithm in the estimation of conflicting dips.

One important application of slope is structural filtering. The basics of the structural filtering is to create a local window along the structural direction and then apply a mean/median filter within this local window. \new{Liu et al. (2010)} \cite{liuyang2010} proposed a trace-prediction way to create local windows along the structure direction by creating a third dimension with predicted traces following the slope. Gan et al. (2016) \cite{shuwei2016somf} developed a structure-oriented median filtering method to suppress the blending noise arise from the simultaneous-source acquisition, where the slope is estimated by transforming the NMO-picked velocities to the slope. Chen et al. (2019) \cite{sosvmf} developed a structure-oriented space-varying median filtering method to deal with the problem of unflattened events in the third  dimension when the slope of seismic data is not accurately estimated.

Another important application of slope is to regularize the inversion-based seismic imaging approaches, e.g., the least-squares reverse time migration (LSRTM) and full waveform inversion (FWI). Xue et al. (2016) \cite{zhiguang2016} developed a constrained LSRTM method to deal with the intense migration artifacts caused by the simultaneous-source shooting or insufficient spatial data sampling, where the smoothing operator along the structural direction is used as a shaping operator to constrain the smoothness of the geological structures. Qu et al. (2019) \cite{qushan2019geo} developed a directional total variation (DTV) method to constrain the velocity model during the FWI iteration so as to avoid being trapped into a local minimum. The DTV constraint is equivalent to the rotated traditional total variation following the dip angle of the geological structure.

Generally speaking, the PWD method has been a well-known slope estimation method in the exploration seismic community. However, the low anti-noise ability of the PWD method still limits its wide application in challenging situations where the random noise is strong \cite{curveletieee2016,yanan2014,weilin2017dlsp,shaohuan2018ieee,zhaoqiang2019tgrs,wang2019hankel}. From the parameter setting perspective, it is usually required to choose a large smoothing radius when dealing with a low signal-to-noise ratio so that the resulted local slope is sufficiently smooth, i.e., avoiding the unstable solution. However, a larger smoothing radius could degrade the fidelity of the estimated slope, resulting in a poor structural processing or constraint when applied subsequently for other tasks. Thus, the stationary fixed smoothing radius is rigid in tuning the performance of the PWD method. In this paper, we developed a novel non-stationary slope estimation method, where the triangle smoother used to regularize the smoothness of the slope is stretched and squeezed according to the signal reliability and complexity. For areas with higher signal reliability or a simpler structural complexity, we use a relatively smaller radius, and vice versa. More importantly, we introduce an adaptive smoothing radius estimation method based on an iterative optimization model. The non-stationary slope estimation with the adaptively estimated smoothing radius is tested via several synthetic and field datasets, which demonstrate a great potential of the proposed method in obtaining better performance in structurally filtering complex seismic data.

@@

Equation \ref{eq:plane2} can be further transformed into the Z-transform notation as: 
\begin{equation}
\label{eq:Z}
A(Z_t,Z_x) D(Z_t,Z_x) = 0,
\end{equation}
where 
\begin{equation}
\label{eq:Z1}
A(Z_t,Z_x) = (1-Z_x\frac{L(Z_t)}{L(1/Z_t)}),
\end{equation}
or 
\begin{equation}
\label{eq:Z2}
H(Z_t,Z_x) D(Z_t,Z_x) = 0,
\end{equation}
where 
\new{\begin{equation}
\label{eq:Z3}
H(Z_t,Z_x) = (L(1/Z_t)-Z_xL(Z_t)),
\end{equation}}
$A(Z_t,Z_x)$ and $H(Z_t,Z_x)$ are two different forms of the plane-wave destruction filter in the Z-transform domain. $L(Z_t)/L(1/Z_t)$ is referred to as the Thiran all-pass filter \cite{thiran1971recursive,fomel2002pwd,zhonghuan2013accelerated}.

@@

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hyper}
   \label{fig:hyper}}
   \subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hyper-n}
   \label{fig:hyper-n}}
\caption{Synthetic test. (a) Clean data. (b) Noisy data (SNR=1.56 dB). }
\label{fig:hyper,hyper-n}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hyper-dip}
  \label{fig:hyper-dip}}
  \subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-dip}
  \label{fig:hypern-dip}}\\
\subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-dip2}
  \label{fig:hypern-dip2}}
  \subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-dip3}
  \label{fig:hypern-dip3}}
\caption{Slope estimation results. (a) Estimated slope from the clean data with a constant smoothing radius $R=5$. (b) Estimated slope from the noisy data with a constant smoothing radius $R=8$. (c) Estimated slope from the noisy data with a constant smoothing radius $R=50$. (d) Estimated slope from the noisy data with the non-stationary smoothing radius map shown in Fig. \ref{fig:rectdip1}. Note that (b) and (c) use the smallest and largest smoothing radii of the non-stationary smoothing radius map. }
\label{fig:hyper-dip,hypern-dip,hypern-dip2,hypern-dip3}
\end{figure}

\begin{figure}[htb!]
 \centering
 \includegraphics[width=\columnwidth]{hyper/Fig/rectdip1}
  \caption{Adaptively estimated smoothing radius for non-stationary dip estimation.}
  \label{fig:rectdip1}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm1}
   \label{fig:hypern-sm1}}
   \subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm2}
   \label{fig:hypern-sm2}}\\
\subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm3}
   \label{fig:hypern-sm3}}
   \subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm4}
   \label{fig:hypern-sm4}}\\
\caption{Smoothing test. (a) Structurally smoothed using the slope estimated from the clean data (SNR=13.73 dB). (b) Structurally smoothed using the slope estimated from the noisy data with a small constant smoothing radius (SNR=11.80 dB). (c) Structurally smoothed using the slope estimated from the noisy data with a large constant smoothing radius (SNR=10.71 dB). (d) Structurally smoothed using the slope estimated from the noisy data with non-stationary smoothing radius (SNR=13.11 dB).}
\label{fig:hypern-sm1,hypern-sm2,hypern-sm3,hypern-sm4}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm1-n}
   \label{fig:hypern-sm1-n}}
   \subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm2-n}
   \label{fig:hypern-sm2-n}}\\
\subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm3-n}
   \label{fig:hypern-sm3-n}}
   \subfigure[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm4-n}
   \label{fig:hypern-sm4-n}}\\
\caption{Smoothing test. (a)-(d) Removed noise corresponding to Figs. \ref{fig:hypern-sm1}-\ref{fig:hypern-sm4}.}
\label{fig:hypern-sm1-n,hypern-sm2-n,hypern-sm3-n,hypern-sm4-n}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-0}
   \label{fig:g-0}}
   \subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-z-a}
   \label{fig:g-z-a}}
\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-z-b}
   \label{fig:g-z-b}}
\caption{Field data example. (a) Raw field data. (b) Zoomed section A. (c) Zoomed section B.}
\label{fig:g-0,g-z-a,g-z-b}
\end{figure}

\begin{figure}[htb!]
\centering
\includegraphics[width=0.45\textwidth]{real2d/Fig/g-rectdip1}
\caption{Field data example. Non-stationary smoothing radius.}
\label{fig:g-rectdip1}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-dip1}
   \label{fig:g-dip1}}
   \subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-dip2}
   \label{fig:g-dip2}}
\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-dip3}
   \label{fig:g-dip3}}
\caption{Smoothing test of the field data example. (a) Slope estimated from the noisy data with a small constant smoothing radius $R=8$. (b) Slope estimated from the noisy data with a large constant smoothing radius $R=100$. (c) Slope estimated from the noisy data with non-stationary smoothing radius.}
\label{fig:g-dip1,g-dip2,g-dip3}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm1-0}
  \label{fig:g-sm1-0}}
  \subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm2-0}
  \label{fig:g-sm2-0}}
\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm3-0}
  \label{fig:g-sm3-0}}
\caption{Smoothing test of the field data example. (a) Structurally smoothed using the slope estimated from the noisy data with a small constant smoothing radius. (b) Structurally smoothed using the slope estimated from the noisy data with a large constant smoothing radius. (c) Structurally smoothed using the slope estimated from the noisy data with non-stationary smoothing radius.}
\label{fig:g-sm1-0,g-sm2-0,g-sm3-0}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm1-n}
  \label{fig:g-sm1-n}}
  \subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm2-n}
  \label{fig:g-sm2-n}}
\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm3-n}
  \label{fig:g-sm3-n}}
\caption{Smoothing test of the field data example. (a)-(c) Removed noise corresponding to Figs. \ref{fig:g-sm1-0}-\ref{fig:g-sm3-0}.}
\label{fig:g-sm1-n,g-sm2-n,g-sm3-n}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm1-z-a0}
 \label{fig:g-sm1-z-a0}}
 \subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm2-z-a0}
 \label{fig:g-sm2-z-a0}}
\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm3-z-a0}
 \label{fig:g-sm3-z-a0}}
\caption{Zoomed comparison of the field data example (frame box A). (a) Structurally smoothed using the slope estimated from the noisy data with a small constant smoothing radius. (b) Structurally smoothed using the slope estimated from the noisy data with a large constant smoothing radius. (c) Structurally smoothed using the slope estimated from the noisy data with non-stationary smoothing radius.}
\label{fig:g-sm1-z-a0,g-sm2-z-a0,g-sm3-z-a0}
\end{figure}

\begin{figure}[htb!]
\centering
\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm1-z-b0}
  \label{fig:g-sm1-z-b0}}
  \subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm2-z-b0}
  \label{fig:g-sm2-z-b0}}
\subfigure[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm3-z-b0}
  \label{fig:g-sm3-z-b0}}
\caption{Zoomed comparison of the field data example (frame box B). (a) Structurally smoothed using the slope estimated from the noisy data with a small constant smoothing radius. (b) Structurally smoothed using the slope estimated from the noisy data with a large constant smoothing radius. (c) Structurally smoothed using the slope estimated from the noisy data with non-stationary smoothing radius.}
\label{fig:g-sm1-z-b0,g-sm2-z-b0,g-sm3-z-b0}
\end{figure}

>>>>

\published{IEEE TGRS, 86, no. 3, W21-W30, (2021)}
\title{obust non-stationary local slope estimation}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\author{Hang Wang\footnotemark[1], Guangtan Huang\footnotemark[1], and Yangkang Chen\footnotemark[1]}

\address{
\footnotemark[1]
School of Earth Sciences\\
Zhejiang University\\
Hangzhou, Zhejiang Province, China, 310027\\
chenyk2016@gmail.com \\}

\righthead{Non-stationary local slope estimation}

@@

%\begin{keywords}
%Seismic signal analysis, structural filtering, local slope
%\end{keywords}

\section{Introduction}
The local slope is a seismic attribute that can be extracted from the raw data. It has been successfully applied in several geophysical processing and inverse problems, e.g., wavefield separation \cite[]{harlan1984signal,fomel2002pwd}, predictive painting \cite[]{fomel2010predictive}, velocity-independent seismic imaging \cite[]{fomel2007velocity}, regularized geophysical inversion \cite[]{fomel2007shape}, etc.

\new{The local slope is closely related with the seismic dip angle. Researchers have started the seismic dip estimation from last century. There are at least three-generations methods for calculating the seismic dip \cite[]{chopra2007volumetric}, e.g., (1) cross-correlation based methods \cite[]{browaeys2010local,aqrawi2012hybrid,aarre2013consistent}, (2) semblance-based discrete scanning methods \cite[]{marfurt19983,lou2019accurate}, (3) structure tensor-based methods \cite[]{hale2007local,wu2017directional,wang2018robust}.}

In the past decades, there have been a variety of slope estimation methods \new{based on the plane-wave theory}. The plane-wave destruction (PWD) method was originally proposed by \cite{claerbout1992pvi}. \cite{fomel2002pwd} proposed to use an implicit finite difference scheme to discretize the plane-wave equation, where an infinite impulse response (IIR) filter (also known as the all-pass filter) to approximate the phase-shift operator and transforms the plane-wave equation into a non-linear inverse problem. Hale (2007) \cite{hale2007local} proposed the structure-tensor, also known as the gradient tensor \cite{van1995estimators}, \old{based slope estimation method based}\new{where the slope estimation is based} on the assumption that eigenvector corresponding to the largest eigenvalue of the structure tensor \old{point}\new{points} to the structural direction.  \cite{liuyang2015} took advantage of the relation between 2D Hilbert transform and the derivatives of the seismic data and derive a fast non-iterative dip estimation method, which turns to be more robust than the PWD based slope estimation method in the case of noisy data \cite{yangkang2018gji3}. \cite{zhonghuan2013accelerated} accelerated the PWD method by deriving an analytical solution to the non-linear inverse problem based on the three-point all-pass approximation filter, thus the PWD method no longer requires outer-loop non-linear iterations and thus is significantly accelerated. \cite{zhonghuan2013omnidirectional} further improved the conventional PWD algorithm by proposing a circle-interpolating model that makes the PWD method avoid the aliasing issues, thereby well handling both vertical and horizontal structures.

The local slope of a seismic data can be used to compress the seismic events along the slope direction, i.e., to obtain an optimally sparse representation of the seismic data. This sparsification process is referred to as the seislet transform \cite[]{fomel2010seislet}. Since the seislet transform is based on the structure direction to compress the data, its sparsity in the transform domain highly depends on the accuracy of the estimated local slope. \cite{yangkang2016emd} discussed the influence of the error of local slope estimation in the sparsity performance of the seislet transform, and developed a dip-separated processing strategy to deal with the limitation of the PWD algorithm in the estimation of conflicting dips.

One important application of slope is structural filtering. The basics of the structural filtering is to create a local window along the structural direction and then apply a mean/median filter within this local window. \cite{liuyang2010} proposed a trace-prediction way to create local windows along the structure direction by creating a third dimension with predicted traces following the slope. \cite{shuwei2016somf} developed a structure-oriented median filtering method to suppress the blending noise arise from the simultaneous-source acquisition, where the slope is estimated by transforming the NMO-picked velocities to the slope. \cite{sosvmf} developed a structure-oriented space-varying median filtering method to deal with the problem of unflattened events in the third  dimension when the slope of seismic data is not accurately estimated.

Another important application of slope is to regularize the inversion-based seismic imaging approaches, e.g., the least-squares reverse time migration (LSRTM) and full waveform inversion (FWI). \cite{zhiguang2016} developed a constrained LSRTM method to deal with the intense migration artifacts caused by the simultaneous-source shooting or insufficient spatial data sampling, where the smoothing operator along the structural direction is used as a shaping operator to constrain the smoothness of the geological structures. \cite{qushan2019geo} developed a directional total variation (DTV) method to constrain the velocity model during the FWI iteration so as to avoid being trapped into a local minimum. The DTV constraint is equivalent to the rotated traditional total variation following the dip angle of the geological structure.

Generally speaking, the PWD method has been a well-known slope estimation method in the exploration seismic community. However, the low anti-noise ability of the PWD method still limits its wide application in challenging situations where the random noise is strong \cite[]{curveletieee2016,yanan2014,weilin2017dlsp,shaohuan2018ieee,zhaoqiang2019tgrs,wang2019hankel}. From the parameter setting perspective, it is usually required to choose a large smoothing radius when dealing with a low signal-to-noise ratio so that the resulted local slope is sufficiently smooth, i.e., avoiding the unstable solution. However, a larger smoothing radius could degrade the fidelity of the estimated slope, resulting in a poor structural processing or constraint when applied subsequently for other tasks. Thus, the stationary fixed smoothing radius is rigid in tuning the performance of the PWD method. In this paper, we developed a novel non-stationary slope estimation method, where the triangle smoother used to regularize the smoothness of the slope is stretched and squeezed according to the signal reliability and complexity. For areas with higher signal reliability or a simpler structural complexity, we use a relatively smaller radius, and vice versa. More importantly, we introduce an adaptive smoothing radius estimation method based on an iterative optimization model. The non-stationary slope estimation with the adaptively estimated smoothing radius is tested via several synthetic and field datasets, which demonstrate a great potential of the proposed method in obtaining better performance in structurally filtering complex seismic data.

@@

Equation \ref{eq:plane2} can be further transformed into the Z-transform notation as: 
\begin{equation}
\label{eq:Z}
A(Z_t,Z_x) D(Z_t,Z_x) = 0,
\end{equation}
where 
\begin{equation}
\label{eq:Z1}
A(Z_t,Z_x) = (1-Z_x\frac{L(Z_t)}{L(1/Z_t)}),
\end{equation}
or 
\begin{equation}
\label{eq:Z2}
H(Z_t,Z_x) D(Z_t,Z_x) = 0,
\end{equation}
where 
\new{\begin{equation}
\label{eq:Z3}
H(Z_t,Z_x) = (L(1/Z_t)-Z_xL(Z_t)),
\end{equation}}
$A(Z_t,Z_x)$ and $H(Z_t,Z_x)$ are two different forms of the plane-wave destruction filter in the Z-transform domain. $L(Z_t)/L(1/Z_t)$ is referred to as the Thiran all-pass filter \cite[]{thiran1971recursive,fomel2002pwd,zhonghuan2013accelerated}.

@@

\begin{figure}[htb!]
\centering
\subfloat[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hyper}
   \label{fig:hyper}}
   \subfloat[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hyper-n}
   \label{fig:hyper-n}}
\caption{Synthetic test. (a) Clean data. (b) Noisy data (SNR=1.56 dB). }
\label{fig:hyper,hyper-n}
\end{figure}

%\begin{figure}[htb!]
%\centering
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hyper-dip}
%  \label{fig:hyper-dip}}
%  \subfloat[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-dip}
%  \label{fig:hypern-dip}}\\
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-dip2}
%  \label{fig:hypern-dip2}}
%  \subfloat[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-dip3}
%  \label{fig:hypern-dip3}}
%\caption{Slope estimation results. (a) Estimated slope from the clean data with a constant smoothing radius $R=5$. (b) Estimated slope from the noisy data with a constant smoothing radius $R=8$. (c) Estimated slope from the noisy data with a constant smoothing radius $R=50$. (d) Estimated slope from the noisy data with the non-stationary smoothing radius map shown in Fig. \ref{fig:rectdip1}. Note that (b) and (c) use the smallest and largest smoothing radii of the non-stationary smoothing radius map. }
%\label{fig:hyper-dip,hypern-dip,hypern-dip2,hypern-dip3}
%\end{figure}

%\begin{figure}[htb!]
% \centering
% \includegraphics[width=\columnwidth]{hyper/Fig/rectdip1}
%  \caption{Adaptively estimated smoothing radius for non-stationary dip estimation.}
%  \label{fig:rectdip1}
%\end{figure}

%\begin{figure}[htb!]
%\centering
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm1}
%   \label{fig:hypern-sm1}}
%   \subfloat[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm2}
%   \label{fig:hypern-sm2}}\\
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm3}
%   \label{fig:hypern-sm3}}
%   \subfloat[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm4}
%   \label{fig:hypern-sm4}}\\
%\caption{Smoothing test. (a) Structurally smoothed using the slope estimated from the clean data (SNR=13.73 dB). (b) Structurally smoothed using the slope estimated from the noisy data with a small constant smoothing radius (SNR=11.80 dB). (c) Structurally smoothed using the slope estimated from the noisy data with a large constant smoothing radius (SNR=10.71 dB). (d) Structurally smoothed using the slope estimated from the noisy data with non-stationary smoothing radius (SNR=13.11 dB).}
%\label{fig:hypern-sm1,hypern-sm2,hypern-sm3,hypern-sm4}
%\end{figure}

%\begin{figure}[htb!]
%\centering
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm1-n}
%   \label{fig:hypern-sm1-n}}
%   \subfloat[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm2-n}
%   \label{fig:hypern-sm2-n}}\\
%\subfloat[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm3-n}
%   \label{fig:hypern-sm3-n}}
%   \subfloat[]{\includegraphics[width=0.45\columnwidth]{hyper/Fig/hypern-sm4-n}
%   \label{fig:hypern-sm4-n}}\\
%\caption{Smoothing test. (a)-(d) Removed noise corresponding to Figs. \ref{fig:hypern-sm1}-\ref{fig:hypern-sm4}.}
%\label{fig:hypern-sm1-n,hypern-sm2-n,hypern-sm3-n,hypern-sm4-n}
%\end{figure}
\inputdir{hyper}
\multiplot{2}{hyper,hyper-n}{width=0.45\textwidth}{Synthetic test. (a) Clean data. (b) Noisy data (SNR=1.56 dB). }

\multiplot{4}{hyper-dip,hypern-dip,hypern-dip2,hypern-dip3}{width=0.45\textwidth}{Slope estimation results. (a) Estimated slope from the clean data with a constant smoothing radius $R=5$. (b) Estimated slope from the noisy data with a constant smoothing radius $R=8$. (c) Estimated slope from the noisy data with a constant smoothing radius $R=50$. (d) Estimated slope from the noisy data with the non-stationary smoothing radius map shown in Fig. \ref{fig:rectdip1}. Note that (b) and (c) use the smallest and largest smoothing radii of the non-stationary smoothing radius map. }

\plot{rectdip1}{width=0.45\textwidth}{Adaptively estimated smoothing radius for non-stationary dip estimation.}

\multiplot{4}{hypern-sm1,hypern-sm2,hypern-sm3,hypern-sm4}{width=0.45\textwidth}{Smoothing test. (a) Structurally smoothed using the slope estimated from the clean data (SNR=13.73 dB). (b) Structurally smoothed using the slope estimated from the noisy data with a small constant smoothing radius (SNR=11.80 dB). (c) Structurally smoothed using the slope estimated from the noisy data with a large constant smoothing radius (SNR=10.71 dB). (d) Structurally smoothed using the slope estimated from the noisy data with non-stationary smoothing radius (SNR=13.11 dB).}

\multiplot{4}{hypern-sm1-n,hypern-sm2-n,hypern-sm3-n,hypern-sm4-n}{width=0.45\textwidth}{Smoothing test. (a)-(d) Removed noise corresponding to Figs. \ref{fig:hypern-sm1}-\ref{fig:hypern-sm4}.}

%\begin{figure}[htb!]
%\centering
%\subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-0}
%   \label{fig:g-0}}
%   \subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-z-a}
%   \label{fig:g-z-a}}
%\subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-z-b}
%   \label{fig:g-z-b}}
%\caption{Field data example. (a) Raw field data. (b) Zoomed section A. (c) Zoomed section B.}
%\label{fig:g-0,g-z-a,g-z-b}
%\end{figure}

%\begin{figure}[htb!]
%\centering
%\includegraphics[width=0.45\textwidth]{real2d/Fig/g-rectdip1}
%\caption{Field data example. Non-stationary smoothing radius.}
%\label{fig:g-rectdip1}
%\end{figure}
%

%\begin{figure}[htb!]
%\centering
%\subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-dip1}
%   \label{fig:g-dip1}}
%   \subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-dip2}
%   \label{fig:g-dip2}}
%\subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-dip3}
%   \label{fig:g-dip3}}
%\caption{Smoothing test of the field data example. (a) Slope estimated from the noisy data with a small constant smoothing radius $R=8$. (b) Slope estimated from the noisy data with a large constant smoothing radius $R=100$. (c) Slope estimated from the noisy data with non-stationary smoothing radius.}
%\label{fig:g-dip1,g-dip2,g-dip3}
%\end{figure}

%\begin{figure}[htb!]
%\centering
%\subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm1-0}
%  \label{fig:g-sm1-0}}
%  \subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm2-0}
%  \label{fig:g-sm2-0}}
%\subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm3-0}
%  \label{fig:g-sm3-0}}
%\caption{Smoothing test of the field data example. (a) Structurally smoothed using the slope estimated from the noisy data with a small constant smoothing radius. (b) Structurally smoothed using the slope estimated from the noisy data with a large constant smoothing radius. (c) Structurally smoothed using the slope estimated from the noisy data with non-stationary smoothing radius.}
%\label{fig:g-sm1-0,g-sm2-0,g-sm3-0}
%\end{figure}

%\begin{figure}[htb!]
%\centering
%\subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm1-n}
%  \label{fig:g-sm1-n}}
%  \subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm2-n}
%  \label{fig:g-sm2-n}}
%\subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm3-n}
%  \label{fig:g-sm3-n}}
%\caption{Smoothing test of the field data example. (a)-(c) Removed noise corresponding to Figs. \ref{fig:g-sm1-0}-\ref{fig:g-sm3-0}.}
%\label{fig:g-sm1-n,g-sm2-n,g-sm3-n}
%\end{figure}

%\begin{figure}[htb!]
%\centering
%\subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm1-z-a0}
% \label{fig:g-sm1-z-a0}}
% \subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm2-z-a0}
% \label{fig:g-sm2-z-a0}}
%\subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm3-z-a0}
% \label{fig:g-sm3-z-a0}}
%\caption{Zoomed comparison of the field data example (frame box A). (a) Structurally smoothed using the slope estimated from the noisy data with a small constant smoothing radius. (b) Structurally smoothed using the slope estimated from the noisy data with a large constant smoothing radius. (c) Structurally smoothed using the slope estimated from the noisy data with non-stationary smoothing radius.}
%\label{fig:g-sm1-z-a0,g-sm2-z-a0,g-sm3-z-a0}
%\end{figure}

%\begin{figure}[htb!]
%\centering
%\subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm1-z-b0}
%  \label{fig:g-sm1-z-b0}}
%  \subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm2-z-b0}
%  \label{fig:g-sm2-z-b0}}
%\subfloat[]{\includegraphics[width=0.45\textwidth]{real2d/Fig/g-sm3-z-b0}
%  \label{fig:g-sm3-z-b0}}
%\caption{Zoomed comparison of the field data example (frame box B). (a) Structurally smoothed using the slope estimated from the noisy data with a small constant smoothing radius. (b) Structurally smoothed using the slope estimated from the noisy data with a large constant smoothing radius. (c) Structurally smoothed using the slope estimated from the noisy data with non-stationary smoothing radius.}
%\label{fig:g-sm1-z-b0,g-sm2-z-b0,g-sm3-z-b0}
%\end{figure}

\inputdir{real2d}
\multiplot{3}{g-0,g-z-a,g-z-b}{width=0.45\textwidth}{Field data example. (a) Raw field data. (b) Zoomed section A. (c) Zoomed section B.}

\plot{g-rectdip1}{width=0.45\textwidth}{Field data example. Non-stationary smoothing radius.}

\multiplot{3}{g-dip1,g-dip2,g-dip3}{width=0.45\textwidth}{Smoothing test of the field data example. (a) Slope estimated from the noisy data with a small constant smoothing radius $R=8$. (b) Slope estimated from the noisy data with a large constant smoothing radius $R=100$. (c) Slope estimated from the noisy data with non-stationary smoothing radius.}

\multiplot{3}{g-sm1-0,g-sm2-0,g-sm3-0}{width=0.45\textwidth}{Smoothing test of the field data example. (a) Structurally smoothed using the slope estimated from the noisy data with a small constant smoothing radius. (b) Structurally smoothed using the slope estimated from the noisy data with a large constant smoothing radius. (c) Structurally smoothed using the slope estimated from the noisy data with non-stationary smoothing radius.}

\multiplot{3}{g-sm1-n,g-sm2-n,g-sm3-n}{width=0.45\textwidth}{Smoothing test of the field data example. (a)-(c) Removed noise corresponding to Figs. \ref{fig:g-sm1-0}-\ref{fig:g-sm3-0}.}
